Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-12-22 Scripts/Initial_Analysis.Rmd
changed treshold to last year rather than first year

    Final_Result <- mean_sd_index %>%
      filter(year > Hist_y) %>%
      mutate(
        tresh_one = ifelse(trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise),"One",NA),
        tresh_two = ifelse(trend > (historic_sd$hist_mean+(2*historic_sd$noise)) | trend < (historic_sd$hist_mean-(2*historic_sd$noise)),"Two",NA)
      ) %>%
      gather("tresh","YesNo",tresh_one,tresh_two) %>% 
      filter(!is.na(YesNo)) %>% 
      group_by(taxon_key,neighbour_id,n_ens,tresh) %>%
      summarise(emerging_yr= min(year)) %>%
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr,tresh)

>>>>

    Final_Result <- mean_sd_index %>%
      filter(year > Hist_y) %>%
      mutate(
        tresh_one = ifelse(trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise),"One",NA),
        tresh_two = ifelse(trend > (historic_sd$hist_mean+(2*historic_sd$noise)) | trend < (historic_sd$hist_mean-(2*historic_sd$noise)),"Two",NA)
      ) %>%
      gather("tresh","YesNo",tresh_one,tresh_two) %>% 
      filter(!is.na(YesNo)) %>% 
      group_by(taxon_key,neighbour_id,n_ens,tresh) %>%
      # summarise(emerging_yr= min(year)) %>% # First year that treshold is crossed
      summarise(emerging_yr= max(year)) %>% # Last year that treshold is crossed
      left_join(EEZ_ids,
                by = "neighbour_id") %>%
      ungroup() %>%
      select(taxon_key,eez_name,eez_neighbour,n_ens,emerging_yr,tresh)
